Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-06-24 doc/paper.Rmd
save .tiff in addition to embedded .png

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.path = "figures/",
	dev = "tiff",
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>",
	dpi = 300
)
library(targets)
library(tidyverse)
library(tsibble)
library(lubridate)
library(knitr)
library(here)
library(patchwork)
```

```{r load-targets}
withr::with_dir(here::here(), {
  tar_load(c(
    # eda_plot,
    # surv_curve,
    # s_spei_plot,
    # g_spei_plot,
    # f_spei_plot,
    # size_plot,
    model_data,
    xa_spei
  ))
})
```

@@

```{r eda, fig.cap=eda_cap, fig.width=7, fig.height=7}
tar_read(eda_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-curve, fig.cap=surv_curve_cap, fig.width=7, fig.height=3.5}
tar_read(surv_curve) + theme(text = element_text(size = 10))
```

@@

@@

@@

@@

@@

\newpage

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.path = "figures/",
	dev = "png",
	dpi = 300,
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>"
)
library(targets)
library(tidyverse)
library(tsibble)
library(lubridate)
library(knitr)
library(here)
library(patchwork)
```

```{r load-targets}
withr::with_dir(here::here(), {
  tar_load(c(
    model_data,
    xa_spei
  ))
})
```

@@

```{r eda, fig.cap=eda_cap, fig.height=7, fig.width=7}
tar_read(eda_plot) & theme(text = element_text(size = 10))
```

<!-- high res version -->

```{r eda_hires, fig.height=7, fig.width=7, dev='tiff', include=FALSE}
tar_read(eda_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-curve, fig.cap=surv_curve_cap, fig.height=3.5, fig.width=7}
tar_read(surv_curve) + theme(text = element_text(size = 10))
```

<!-- high res version -->

```{r surv-curve_hires, fig.height=3.5, fig.width=7, dev="tiff", include=FALSE}
tar_read(surv_curve) + theme(text = element_text(size = 10))
```

@@

<!-- high res version -->

```{r size-plot_hires, fig.width=7, fig.height=7, dev='tiff', include=FALSE}
tar_read(size_plot) & theme(text = element_text(size = 10))
```

@@

<!-- high res version-->

```{r surv-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', include=FALSE}
tar_read(s_spei_plot) & theme(text = element_text(size = 10))
```

@@

<!-- high res version -->

```{r growth-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', include=FALSE}
tar_read(g_spei_plot) & theme(text = element_text(size = 10))
```

@@

<!-- high res version-->

```{r flwr-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', include=FALSE}
tar_read(f_spei_plot) & theme(text = element_text(size = 10))
```

@@
